
\cvsection{Education}
\cvevent{PhD in Bioengineering and Robotics}{Istituto Italiano di Tecnologia \& University of Genova}{Jul 2022}{}
\textbf{International Doctorate} \textit{summa cum laude}

\divider

\cvevent{BSc \& MSc in Computer Engineering}{University of Bologna}{Dec 2015 \& Mar 2018}{}
\textbf{MSc:} 110/110 \textit{summa cum laude}\\ 
\textbf{BSc:} 101/110

% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

\cvsection{Projects}
\cvproject{Lie Detection in HRI}
\begin{itemize}
\item Machine Learning model to autonomously detect lies based on a real-time pupillometry-based cognitive load evaluation. Implemented on the humanoid robot iCub and tested both in a lab and in real-environments (Maker Faire Rome 2022) leveraging interactive online learning.
\end{itemize}
\smallskip


\cvproject{Social Engineering Adventure (SEA)}
\begin{itemize}
\item Python textual adventure to challenge players against Social Engineering threats. Real-time control of the humanoid robot iCub (in C++). Multi-modal acquisition and processing of physiological data from an Eyelink 1000, a Tobii Pro Glasses 2 and a Shimmer3 GSR+, used to predict humans' compliance.
\end{itemize}
\smallskip

\cvproject{Adventurer Robot Companion (ARC)}
\begin{itemize}
\item Evolution of the SEA project developed during a Visiting Research period at the University of Waterloo (Canada). Exploration of different intervention strategies to prevent humans' compliance using the Furhat robot.
\end{itemize}
\smallskip

\cvproject{Unreliable Treasure Hunt}
\begin{itemize}
\item On-the-wild human-robot interaction to analyse the building and evolution of trust between a human and a robot. Participants have to find 6 eggs hidden in a room, asking hints to iCub which eventually show technical failures.
\end{itemize}
\smallskip

\cvproject{Endless Upgrade}
\begin{itemize}
\item Master's Degree dissertation project @ Data Reply. I used DevOps principles and tools (Ansible, Terraform, Jenkins) to fully automatise the development and deployment process of a movie recommendation service in a Big Data ecosystem.
\end{itemize}
\smallskip
\smallskip
\cvproject{}